%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{setup-class}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
\name{Cory}{Maloy}
\position{Senior Full Stack Software Engineer{\enskip\cdotp\enskip}Philosopher}
\address{21167 NW Galice Lane Apt. 308, Portland Oregon, 97229 USA}
\mobile{(+1) 541-315-0057}
\email{corymaloy@hotmail.com}
%\homepage{www.corymaloy.com}
\github{chlorophant}
\linkedin{cory-maloy}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}
  {CBT Nuggets LLC\\550 Valley River Drive\\Eugene, OR 97401}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Senior Software Engineer - Bend}
% How the letter is opened
\letteropening{Dear Hiring Manager,}

% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Cory R. Maloy~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I'm an experienced full stack software engineer with 5 years of enterprise software experience, resulting in several successfully completed projects and happy clients. I'm knowledgeable in most of today’s popular technologies, especially React, Node, Golang, Docker, Kubernetes, and various cloud provider APIs including AWS, Google Cloud, and Digital Ocean. Able to work independently or as a member of a team to effectively produce results and meet client expectations. I have a strong sense of responsibility and duty. I'm a quick learner with drive and passion to succeed in almost any scenario. I’m looking for opportunities to learn new technologies, grow, and perfect my craft. 

\lettersection{Why CBT Nuggets?}
CBT Nuggets is a very appealing place for me, after spending the last two years building payment and billing services, dealing with very sensitive insurance claims data, and generally unhappy users (medical bills). I have a new appreciation for building simple solutions, with clear value propositions, which actually make users happy. I genuinely find the concept of helping fellow techies to learn complicated topics to be very attractive. I believe it will bring me a sense of fulfillment. Additionally, an old coworker has highly recommended CBT Nuggets as a great place to work, and I trust their assessment.

\lettersection{Why Me?}
I've worked very hard to grow my career quickly. If you look at my resume, you will see I went from entry level to a senior engineer in about three years. That was not by chance, that was from sheer will, overtime, and dedication to perfecting my skills. I spent evenings and weekends learning in order to give me the edge in my job. I want to make sure you know that I am dedicated and hard working. I'm serious about improving myself and am constantly trying to become a "10x engineer". I'm not sure if I will ever reach that goal, but I do not intend to stop trying. I believe the attributes and skills I posses stand to benefit your organization and I hope you will consider my for the position.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
